---
title: "Quarto revealjs custom theme"
subtitle: "Subtitle goes here"
author: "Joseph V. Casillas"
institute: "Rutgers University"
date: "Last update: `r Sys.Date()`"
format: rutgers-revealjs
engine: knitr
execute: 
  out.width: "100%"
  fig.asp: 0.5625
  dpi: 300
---

## The basics

- Similar to `xaringan`, **revealjs** uses \# for headers
- One difference is that they automatically generate a new slide
  - Two (\#\#) for a level two header at the top of a slide
  - One (\#) is centered vertically (good for a section divider)
- All other basic markdown syntax works the same: 

## Incremental slides

To make an ordered or unordered list incremental you have to use css

. . .

</br>

:::: {.columns}

::: {.column width="50%"}
```
::: {.incremental}
- First this one
- Then this one
:::
```
:::

::: {.column width="50%"}
::: {.incremental}
- First this one
- Then this one
:::
:::

::::

. . .

:::: {.columns}

::: {.column width="50%"}
```
::: {.incremental}
1. First this one
2. Then this one
:::
```
:::

::: {.column width="50%"}
::: {.incremental}
1. First this one
2. Then this one
:::
:::

::::



## Multiple columns

You can make multiple columns of any width using css as well

. . .

```
:::: {.columns}

::: {.column width="40%"}
Left column
:::

::: {.column width="60%"}
Right column
:::

::::
```

:::: {.columns}

::: {.column width="50%"}
Left column
:::

::: {.column width="50%"}
Right column
:::

::::


## Long slides? {.smaller}

You can use css to make text smaller with `{.smaller}`

. . .

```
## Slide Title {.smaller}
```

. . .

- this
- is
- ideal
- for 
- really
- long
- slides
- but
- it's
- usally
- better to avoid that


## Long slides? (again) {.scrollable}

Another option is to make the individual slide scrollable using `{.scrollable}`

. . .

- this
- is
- ideal
- for 
- really
- long
- slides
- but
- it's
- usally
- better 
- to 
- avoid 
- that


## Don't forget your speaker notes

You can get your speaker notes all set up using

```
::: {.notes}
Speaker notes go here.
:::
```

Click "s" to see some notes

::: {.notes}
These are some notes.
:::


## Asides

You can include asides, but they are kind of weird. 

```
::: aside
This is an aside
:::
```

::: aside
This is an aside
:::


## Footnotes

I think footnotes are probably more useful ^[But maybe not always]

. . .

You can make them endnotes (ew) like this: 

```
---
format:
  revealjs:
    reference-location: document
---
```


## Custom footers

You can add a custom footer to any slide using

```
::: footer
This is my footer
:::
```

::: footer
This is my footer
:::


## IPA symbols work in unicode

- /ʃæ.'riŋ.ɡæn/

- /θðszʃʒʂʐçʝʎʟɘɵəɜ/


|     Word    | Phonology | Phonetics            |
| :---------- | --------- | -------------------- |
| casa        | /ˈka.sa/  | [ˈka.sa]             |
| taco (Sp.)  | /ˈta.ko/  | [ˈta.ko]             |
| taco (Eng.) | /ˈta.ko/  | [ˈt<sup>h</sup>a.ko] |


## Standard slide with R code {.smaller}

- You can highlight code using `code-line-numbers` in the knitr chunk options
- If you include pipes, e.g., `code-line-numbers: "|5|"` they will be highlighted incrementally (nice!)
- Using `output-location:` (fragment, slide, column, column-fragment) controls when and where the output of the code is displayed

```{r}
#| label: fig-code-ex
#| fig.cap: Example caption.
#| echo: true
#| code-line-numbers: "|1|2|3|4|5|6|"
#| output-location: slide

library("tidyverse")
ggplot(cars) + 
  aes(x = dist, y = speed) + 
  geom_point() + 
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) + 
  theme_bw(base_family = "Palatino", base_size = 20) + 
  theme(
    panel.grid.major = element_line(colour = 'grey90', size = 0.15),
    panel.grid.minor = element_line(colour = 'grey90', size = 0.15)
  )
```


## Tabsets

You can use tabsets pretty easily

```
::: {.panel-tabset}

### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`

:::
```

(example on next slide)



---

::: {.panel-tabset}

### Code

```{r}
#| label: build-fig-tabset
#| echo: true
plot_tabs <- mtcars |>
  ggplot() + 
  aes(x = drat, y = mpg) + 
  geom_point() + 
  geom_smooth(method = lm, formula = "y ~ x") + 
  theme_bw(base_family = "Palatino", base_size = 20) + 
  theme(
    panel.grid.major = element_line(colour = 'grey90', size = 0.15),
    panel.grid.minor = element_line(colour = 'grey90', size = 0.15)
  )
```


### Output

```{r}
#| label: fig-tabset
#| fig.cap: Tabset plot
plot_tabs
```

:::



# Backgrounds {background-color="#000"}




## This is the final slide {background-color="#000"}

### you can add your email, twitter, github, etc. info here

Here is an example:  

|                                                                                                    |                                   |
| :------------------------------------------------------------------------------------------------- | :-------------------------------- |
| <a href="mailto:joseph.casillas@rutgers.edu"><i class="fa fa-paper-plane fa-fw"></i>               | joseph.casillas@rutgers.edu       |
| <a href="http://www.jvcasillas.com/ru_xaringan/slides/index.html"><i class="fa fa-link fa-fw"></i> | jvcasillas.com/ru_xaringan/slides |
| <a href="http://twitter.com/jvcasill"><i class="fa fa-twitter fa-fw"></i>                          | @jvcasill                         |
| <a href="http://github.com/jvcasillas"><i class="fa fa-github fa-fw"></i>                          | @jvcasillas                       |
